\documentclass{article}
\begin{document}

\resumeProjectHeading{\textbf{CareerAutomated}}{}
\resumeItem{Built an autonomous 10-Agent AI platform that finds jobs, researches companies, tailors LaTeX resumes, and submits applications end-to-end with zero human intervention.}
\resumeItem{Implemented component-based architecture separating discovery, intelligence, routing, and execution.}
\resumeItem{Designed human-in-the-loop review gate for safety before final submission.}
\resumeItem{Developed waterfall UI normalization strategy (Exact -> Rules -> Fuzzy) to handle modern custom ATS widgets like React-Select.}
\resumeItem{Built embedding-free RAG using BM25 for zero-cost, high-speed knowledge retrieval.}
\resumeItem{Implemented strict prompt grounding rules and low-confidence gating to prevent LLM hallucinations on business metrics.}

\resumeProjectHeading{\textbf{AI Data Analyst Agent}}{}
\resumeItem{Designed a 5-agent LangGraph system where non-technical users type a question in plain English and get a data analysis result in under 60 seconds — no SQL, no engineer required.}
\resumeItem{Implemented LangGraph for stateful agent workflow (not vanilla LangChain) — explicit state management per agent.}
\resumeItem{Query Planner does intent classification BEFORE generation — eliminates downstream type errors.}
\resumeItem{Used n8n as orchestration layer separate from agent logic — non-technical operators can modify routing without redeployment.}
\resumeItem{Implemented MCP to expose tools (files, DBs, APIs) as standardised context — extensible by design.}
\resumeItem{Designed Error Fixer agent: classify exception → regenerate targeted fix → retry 3x before user escalation (ReAct-style).}
\resumeItem{Used Docker sandbox to isolate LLM-generated code from host.}

\resumeProjectHeading{\textbf{Backend Systems}}{}
\resumeItem{Deployed FastAPI + Docker + AWS EC2 for scalable backend infrastructure.}
\resumeItem{Implemented SQL for analytical queries (funnel, cohort, window functions).}
\resumeItem{Used Python for data and backend development.}

\resumeProjectHeading{\textbf{OrangeLabs Internship}}{}
\resumeItem{Contributed to CCTV-based automated attendance (computer vision pipeline → ERP sync).}
\resumeItem{Developed AI-generated personalised lecture pipeline (teacher voice/likeness cloning for student-facing content).}
\resumeItem{Implemented n8n ERP workflow automation (weaker signal, de-emphasised).}

\end{document}